systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2005-11-02 paper/trunk/systemfit.tex
small last changes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@579 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%% an abstract and keywords
\Abstract{Many statistical analysis are based on sets of models that
  consist of  more than one equation which contain relationships among
  the various equations.  Ignoring these relationships can result in
  biased and possibly inconsistent parameter estimates. These sets of
  equations should be fitted simultaneously rather than equation  by
  equation.  The package \pkg{systemfit} provides the capability to
  estimate systems of linear and non-linear equations, using limited
  and full-information methods within the \proglang{R} programming
  environment.  }

@@

\section{CVS Revision Log}
\begin{verbatim}
$Log$
Revision 1.15  2005/11/02 18:15:40  hamannj
small changes

Revision 1.14  2005/10/26 21:16:53  hamannj
checked out and updated local copy before edits

Revision 1.13  2005/09/26 20:34:12  henningsena
using now package csquotes to have uniform and correct quotation marks (BibTeX-Style jss.bst has to be modified)

Revision 1.12  2005/09/26 11:24:05  henningsena
some minor changes

Revision 1.11  2005/09/01 12:27:55  henningsena
revised structure of the document (sections, subsections, subsubsections) due to removal of nlsystemfit; moved each section into a separate file.

Revision 1.10  2005/09/01 11:49:02  henningsena
moved section about non-linear estimation from systemfit.tex into new file nlsystemfit.tex, because this section should not be included in (this version of) the article

Revision 1.9  2004/11/16 10:59:09  henningsena
some minor changes and some comments on nlsystemfit

Revision 1.8  2004/11/16 08:55:53  henningsena
merged file and resolved conflict due to some minor changes I did while Jeff was adding nlsystemfit.

Revision 1.7  2004/11/16 05:34:47  hamannj
question about nlsystemfit code section (example)

Revision 1.6  2004/11/16 05:32:46  hamannj
made small changes because my code section wouldn't compile. argh.

Revision 1.5  2004/11/16 05:31:19  hamannj
added cvs header and log section. to be removed when submitted.

\end{verbatim}

>>>>

%% an abstract and keywords
\Abstract{Many statistical analysis are based on models that consist
  of  more than one equation. If these models contain relationships
  among the various equations, ignoring these relationships can result
  in biased and possibly inconsistent parameter estimates. If
  relationships exist among the equations, the sets of equations
  should be fitted simultaneously rather than equation by equation.
  The package \pkg{systemfit} provides the capability to estimate
  systems of linear and non-linear equations, using limited and
  full-information methods within the \proglang{R} programming
  environment.  }

@@

% \section{CVS Revision Log}
% \begin{verbatim}
% $Log$
% Revision 1.16  2005/11/02 18:31:45  hamannj
% small last changes
%
% Revision 1.15  2005/11/02 18:15:40  hamannj
% small changes

% Revision 1.14  2005/10/26 21:16:53  hamannj
% checked out and updated local copy before edits

% Revision 1.13  2005/09/26 20:34:12  henningsena
% using now package csquotes to have uniform and correct quotation marks (BibTeX-Style jss.bst has to be modified)

% Revision 1.12  2005/09/26 11:24:05  henningsena
% some minor changes

% Revision 1.11  2005/09/01 12:27:55  henningsena
% revised structure of the document (sections, subsections, subsubsections) due to removal of nlsystemfit; moved each section into a separate file.

% Revision 1.10  2005/09/01 11:49:02  henningsena
% moved section about non-linear estimation from systemfit.tex into new file nlsystemfit.tex, because this section should not be included in (this version of) the article

% Revision 1.9  2004/11/16 10:59:09  henningsena
% some minor changes and some comments on nlsystemfit

% Revision 1.8  2004/11/16 08:55:53  henningsena
% merged file and resolved conflict due to some minor changes I did while Jeff was adding nlsystemfit.

% Revision 1.7  2004/11/16 05:34:47  hamannj
% question about nlsystemfit code section (example)

% Revision 1.6  2004/11/16 05:32:46  hamannj
% made small changes because my code section wouldn't compile. argh.

% Revision 1.5  2004/11/16 05:31:19  hamannj
% added cvs header and log section. to be removed when submitted.

% \end{verbatim}

### 2005-11-02 paper/trunk/systemfit_other.tex
small last changes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@579 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Currently, the \code{systemfit} package can perform a Likelihood Ratio
test to test linear restrictions when estimating SUR equation systems.

This test calculates the likelihood ratio value by calculating the
estimated residual covariance matrix $hat{S}$ by the maximum likelihood
formula

\begin{equation}
hat{s}_{ij} = \frac{\hat{e}_i^{'} \hat{e}_j}{T} 
\end{equation}
where $T$ is vector of ones.

% (no matter which formula is used in the estimation).

You should really get some of the text from your stats book.

>>>>

Currently, the \code{systemfit} package can perform a Likelihood Ratio
test to test linear restrictions when estimating SUR equation systems.
The function returns the empirical likelihood ratio, the $p$-value and
the degrees of freedom of the test which is equivalent to the number
of restrictions.

% This test calculates the likelihood ratio value by calculating the
% estimated residual covariance matrix $\hat{S}$ by the maximum
% likelihood formula,

% \begin{equation}
% \hat{s}_{ij} = \frac{\hat{e}_i^{'} \hat{e}_j}{T} 
% \end{equation}
% where $T$ is vector of ones.
